---
runtime: shiny
output: html_document
---

 Best Soccer club in the world - Case Study
==========================================

## Business motivation
 
## Data Description

```{r, echo=FALSE, message=FALSE, prompt=FALSE, results='asis'}
source("RunStudy.R")
setwd("./doc")

t1 <- gvisTable(gadata[1:100,],options = list(showRowNumber = FALSE, width = 800, height = min(400,27*(nrow(gadata) + 1)), allowHTML = TRUE, page = 'disable'))
print(t1,'chart')

```

## Questions solved

***1. Where do customers come from? Which sites/ads are “feeding" our sales?<br>***
```{r, echo=FALSE, eval=TRUE, message=FALSE, prompt=FALSE, results='asis', tidy=TRUE}

entrppage <-  group_by(gadata, factor(Country)) %>% summarise(Revenues = sum(Revenues))
entrppage = data.frame(pages = entrppage$`factor(Country)`, Revenues = entrppage$Revenues)
top_entrppage = entrppage[sort(entrppage$Revenues, decreasing =  TRUE, index.return = TRUE)$ix,]

t3 <- gvisTable(top_entrppage,options = list(showRowNumber = FALSE, width = 800, height = min(400,27*(nrow(top_entrppage) + 1)), allowHTML = TRUE, page = 'disable'))
print(t3,'chart')

Bubble1 <- gvisBubbleChart(data.frame(gadata5), idvar="Country", yvar="Log_Trans", xvar="Rev_per_trans", colorvar="Revenues",sizevar="Revenues", options = list(showRowNumber = FALSE, width = 1000, height =800,sizeAxis = '{minValue: 0,  maxSize: 100}',axisTitlesPosition="out"))
print(Bubble1,'chart')

```

```{r, echo=FALSE, eval=TRUE, message=FALSE, prompt=FALSE, results='asis'}

entrppage <-  group_by(gadata3, factor(Ciudad)) %>% summarise(Ingresos = sum(Ingresos))
entrppage = data.frame(cities = entrppage$`factor(Ciudad)`, Ingresos = entrppage$Ingresos)
top_entrppage = entrppage[sort(entrppage$Ingresos, decreasing =  TRUE, index.return = TRUE)$ix,]

sliderInput("high", "Highest Buyers:", min = 1, max = 200, value = c(1,25))

renderPlot({

ll.cities <- geocode(as.character(top_entrppage[(input$high[1]):(input$high[2]),1]))
visit.x <- ll.cities$lon
visit.y <- ll.cities$lat

mp <- NULL
mapWorld <- borders("world", colour="gray50", fill="gray50") # create a layer of borders
mp <- ggplot() +   mapWorld

mp <- mp+ geom_point(aes(x=visit.x, y=visit.y) ,color="blue", size=2) 
mp
})

```

  Considering websites, total sales come from:<br>
    •	69% organic (search engines, 64% google, 2% bing, 1% yahoo, 1% navers, 1% others)<br>
    •	26% direct<br>
    •	5% others<br>
  Regarding geography, sales come from:<br>
    •	71% Spain<br>
    •	5% UK<br>
    •	3% France<br>
    •	3% Germany and Switz. <br>     
    •	2% USA<br>
    •	16% others<br>
***2. Which combinations of sources and mediums attract the more amount of new visitors?***<br>
  •	54% organic (search engines, 51% google, 1% bing, 1% yahoo, 0,5% navers, 0,5% others)<br>
  •	36% direct<br>
  •	3% t.co, referral (twitter)<br>
  •	2% m.facebook.com and facebook.com, referral<br>
  •	4% others<br>
***3. Is there a correlation between the time a page takes to load and sales? (Are we loosing clients because the site doesn’t load?)***<br>
  •	In a first analysis it seems that there is a 0.67 correlation between Transactions and Loading time<br>
  •	However, when one builds a linear regression on the most significant variables (significance level=5%)<br>
  •	Linear regression shows 0 coefficient for load time and a relatively small coefficient for ln(Load time), but 1 order of magnitude lower than the others<br>
***4. Are people who initially came from banners more likely to buy or not?***<br>
  •	Users that landed on the website coming from banners have zero purchases<br>
***5.	Can we build a model to predict average purchase?***<br>
  •	No, a regression for this would yield R2=8% but the regressions for quantity or total revenues yield R2=99%<br>

## Questions to solve
***6. Adding to the question 1 of where do customer come from: do users in Madrid buy online? Is a significant share of the Spanish buyers from Madrid? Otherwise we can raise the question if the Madrilenos know that they can buy online...***<br>


***7. How do new users find the website? How could the club further spread the brand and increase the number of new users to the website?***<br>
***8. Are ticket buyers already regular visitors to the site? Or are they mostly coming for one time purchase?***<br>
***9. What is the average time spent on the website? What do users do on it?***<br>
***10. Are users accessing from certain brands of computers/smartphones more likely to buy? Or to have a higher Order Average Value?***<br>
***11. Could we find a way to better segment the market of buyers online?***<br>
***12. What are the pages with the highest average time on page? Should we suggest to have more of this content? And do these views lead to sales?***<br>
***13. How could the club further spread the brand? Which dimensions/metrics could we look into to address this? Eg. What is the bounce rate vs some benchmark?*** <br>

## Questions unsolvable due to lack of data
1. Are there products that are typically bought together (e.g. game tickets and sweaters)? Could we work on some bundles? - ***Cannot test***<br>
2. What are the trends in purchases before the matches? - ***Cannot test***<br>
 <br>
 <br>